---
title: "Time Series - ARIMA"
author: "Anton Bazin"
date: "25 12 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Built with R `r getRversion()`.



```{r}
eps <- read.csv('jj.dat', header=FALSE)
head(eps)
```
After obtaining a copy of the dataset, plot the quarterly EPS vs. time.  Describe any patterns that you observe.
```{r}
series <- ts(eps, start=1960, end=1980, frequency=4)
plot(series)
```


In order to perform an ARIMA model, the time series will need to be transformed to remove any trend.

Plot the difference of xt and xt-1, for all t > 0.
- Has this difference adequately detrended the series? ---(No)
- Does the variability of the EPS appear constant over time? ---No
- Why does the constant variance matter? ---Model uses white noise
```{r}
dx1 <- tail(eps, -1) - head(eps, -1)
dx1ts<- ts(dx1, start=1960, end=1980, freq=4)
plot(dx1ts)
summary(head(dx1, 42))  # looking at means - get a clue about trends
summary(tail(dx1, 42))
summary(dx1)
```



Plot the log10 of the quarterly EPS vs. time and plot the difference of
log10(xt ) and log10(xt-1) for all t > 0.
- Has this adequately detrended the series?
- Has the variability of the differenced log10(EPS) become more constant?  
```{r}
log10eps <- log10(eps)
log10ts <- ts(log10eps, start=1960, end=1980, freq=4)
plot(log10ts, main='Log10TS')

dxlog10 <- tail(log10eps, -1) - head(log10eps, -1)
dxlog10ts<- ts(dxlog10, start=1960, end=1980, freq=4)
plot(dxlog10ts, main='dxLog10ts')

summary(head(dxlog10, 42))  # looking at means - get a clue about trends
summary(tail(dxlog10, 42))
summary(dxlog10)
```



Treating the differenced log10 of the EPS series as a stationary series,
plot the ACF and PACF of this series.
What possible ARIMA models would you consider and why?
```{r}
par(mfrow=c(2,1))  # plot together
acf(dxlog10ts)
pacf(dxlog10ts)
```
'Rule 6: If the PACF of the differenced series displays a sharp cutoff and/or
the lag-1 autocorrelation is positive--i.e., 
if the series appears slightly "underdifferenced"--then consider 
adding an AR term to the model.'




Run the proposed ARIMA models from part d and compare the results.
Identify an appropriate model. Justify your choice.   
```{r}
arima1 <- arima(dxlog10ts, order=c(1, 0, 0))
arima2 <- arima(dxlog10ts, order=c(2, 0, 0))
arima3 <- arima(dxlog10ts, order=c(3, 0, 0))
arima4 <- arima(dxlog10ts, order=c(4, 0, 0))  # best
arima5 <- arima(dxlog10ts, order=c(5, 0, 0))
arima6 <- arima(dxlog10ts, order=c(4, 0, 1))
arima7 <- arima(dxlog10ts, order=c(5, 0, 1))
AIC(arima1, arima2, arima3, arima4, arima5, arima6, arima7)
arima4
```

Why is the choice of natural log or log base 10 in Problem 4.8 somewhat
irrelevant to the transformation and the analysis?

--- Not the best method to detrend. Might need to use linear or higher-order functions


Why is the value of the ACF for lag 0 equal to one? 
--- cor with itself = 1 (0th term == itself)



Using arima.sim in R, simulate 10,000 points for AR(p) p = 1,2,3,4.
Plot the simulated series, ACF and PACF.
What pattern emerges between p and the plots?  
```{r}
ars <- arima.sim(n=10000, list(ar=c(-0.6873, -0.6129, -0.6340, 0.2704)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ar=c(-0.6873, -0.6129, -0.6340)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ar=c(-0.6873, -0.6129)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ar=c(-0.6873)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)
```


Using arima.sim in R, simulate 10,000 points for MA(p) p = 1,2,3,4.
Plot the simulated series, ACF and PACF.
What pattern emerges between p and the plots?
```{r}
arima8 <- arima(dxlog10ts, order=c(0, 0, 4))
arima8
```


```{r}
ars <- arima.sim(n=10000, list(ma=c(-0.6552, -0.1804, -0.4048, 0.7546)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ma=c(-0.6552, -0.180,4-0.4048)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ma=c(-0.6552, -0.1804)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)

ars <- arima.sim(n=10000, list(ma=c(-0.6552)))
ts.plot(ars)
par(mfrow=c(2,1))
acf(ars)
pacf(ars)
```

