---
title: "Text Analysis"
author: "Anton Bazin"
date: "25 12 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tm)
library(wordcloud)
library(dplyr)
```

20 news articles with additional meta information from the
Reuters-21578 XML data set.
All documents belong to the topic crude dealing with crude oil.
```{r}
data('crude')
#crude[[2]]$content
article  <- crude[2]
```

Create a word cloud of the 20 most frequent words in this article 
(the 2nd article in the crude corpus).
```{r}
tdm <- TermDocumentMatrix(article)
freqitems <- data.frame(findMostFreqTerms(tdm, 20))
freqitems[2] <- rownames(freqitems)
freqitems
```

```{r}
set.seed(42)
wordcloud(words=freqitems$V2, freq=freqitems$X144, min.freq=1,
          max.words=20, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, 'Dark2'))
```





Again, create a word cloud of the 20 most frequent words in the article.
But this time, remove all stop words, punctuations, and numbers.
```{r}
art <- article
art <- tm_map(art, content_transformer(tolower))
art <- tm_map(art, removeNumbers)
art <- tm_map(art, removeWords, stopwords('english'))
art <- tm_map(art, removePunctuation)


tdm2 <- TermDocumentMatrix(art)
tdmatr <- as.matrix(tdm2)
freqitems2 <- data.frame(findMostFreqTerms(tdm2, 20))
freqitems2[2] <- rownames(freqitems2)
freqitems2
```


```{r}
idf <- log(ncol(as.matrix(tdm2))/( 1 + rowSums(as.matrix(tdm2) != 0))) %>% diag()
tfidf <- crossprod(as.matrix(tdm2), idf)
colnames(tfidf) <- rownames(as.matrix(tdm2))

set.seed(42)
wordcloud(words=colnames(tfidf)[head(order(tfidf), 20)], 
           freq=freqitems2$X144, min.freq=1,
           max.words=40, random.order=FALSE, rot.per=0.35, 
           colors=brewer.pal(8, 'Dark2'))
```




Create a word cloud of 20 words in this article with the highest TF-IDF values.
```{r}
idf <- log(ncol(as.matrix(tdm))/( 1 + rowSums(as.matrix(tdm) != 0))) %>% diag()
tfidf <- crossprod(as.matrix(tdm), idf)
colnames(tfidf) <- rownames(as.matrix(tdm))

set.seed(42)
wordcloud(words=colnames(tfidf)[head(order(tfidf), 20)], 
           freq=freqitems$X144, min.freq=1,
           max.words=40, random.order=FALSE, rot.per=0.35, 
           colors=brewer.pal(8, 'Dark2'))
```


Create a word cloud of 20 words in this article with the highest TF-IDF values,
removing all stop words, punctuations, and numbers.
```{r}
idf <- log(ncol(as.matrix(tdm2))/( 1 + rowSums(as.matrix(tdm2) != 0))) %>% diag()
tfidf <- crossprod(as.matrix(tdm2), idf)
colnames(tfidf) <- rownames(as.matrix(tdm2))

set.seed(42)
wordcloud(words=colnames(tfidf)[head(order(tfidf), 20)], 
           freq=freqitems2$X144, min.freq=1,
           max.words=40, random.order=FALSE, rot.per=0.35, 
           colors=brewer.pal(8, 'Dark2'))
```












