---
title: "Naive Bayes"
author: "Anton Bazin"
date: "13 12 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(e1071)
```


```{r}
df <- read.csv(file ='nbtrain.csv', header = TRUE, sep=',')
train <- df[1:9010,]
test <- df[9011:10010,]
```


Construct the Naïve Bayes classifier from the training data, according to the formula
“income ~ age + sex + educ”.
```{r}
nb <- naiveBayes(as.factor(income) ~ age + sex + educ, train)
nb
# testing
pred <- predict(nb, test)
nbmatr <- table(actual=test$income, predicted = pred)
nbmatr
```


Score the model with the testing data and create the model’s confusion matrix.  
Also, calculate the overall, 10-50K, 50-80K, and GT 80K misclassification rates.
Explain the variation in the model’s predictive power across income classes.
```{r}
# 10-50K
misclass1 <- 1 - nbmatr[1,1]/sum(nbmatr[1,])
misclass1
# 50-80K
misclass2 <- 1 - nbmatr[2,2]/sum(nbmatr[2,])
misclass2
# GT 80K
misclass3 <- 1 - nbmatr[3,3]/sum(nbmatr[3,])
misclass3
# Total
misclasstot <- 1 - sum(diag(nbmatr))/sum(nbmatr)
misclasstot
```


Construct the classifier according to the formula “sex ~ age + educ + income”,
and calculate the overall, female, and male misclassification rates.
Explain the misclassification rates?
```{r}
nb2 <- naiveBayes(as.factor(sex) ~ age + income + educ, train)
nb2

pred2 <- predict(nb2, test)
nbmatr2 <- table(actual=test$sex, predicted = pred2)
nbmatr2
```



```{r}
# F
misclass12 <- 1 - nbmatr2[1,1]/sum(nbmatr2[1,])
misclass12
# M
misclass22 <- 1 - nbmatr2[2,2]/sum(nbmatr2[2,])
misclass22
# Total
misclasstot2 <- 1 - sum(diag(nbmatr2))/sum(nbmatr2)
misclasstot2
```


Divide the training data into two partitions, according to sex, 
and randomly select 3500 records from each partition. 
Reconstruct the model from part (a) from these 7000 records.
Provide the model’s a priori and conditional probabilities.
Repeat step (b) 4 several times.
What effect does the random selection of records have on the model’s performance?
```{r}
for (i in c(1, 2, 3, 4)){
  print('')
  print('')
  print(paste('Iteration ', as.character(i), '--------------------------------------------------------'))
  males <- train[train$sex == 'M',]
  females <- train[train$sex == 'F',]
  males <- males[sample(nrow(males), 3500),]
  females <- females[sample(nrow(females), 3500),]
  
  mf <- rbind(males, females)
  
  nb3 <- naiveBayes(as.factor(sex) ~ age + income + educ, mf)
  print(nb3)
  pred3 <- predict(nb3, test)
  
  nbmatr3 <- table(actual=test$sex, predicted=pred3)
  print(nbmatr3)
  # M
  nb3misclassf <- 1 - nbmatr3[1,1]/sum(nbmatr3[1,])
  print(nb3misclassf)
  # F
  nb3misclassm <- 1 - nbmatr3[2,2]/sum(nbmatr3[2,])
  print(nb3misclassm)
  # M+F
  nb3misclassmf <- 1 - sum(diag(nbmatr3))/sum(nbmatr3)
  print(nb3misclassmf)
}
```


